---
title: "607.TidyVerse"
author: "Marjete Vucinaj"
date: "2022-10-30"
output: html_document
---

Your task here is to Create an Example.  Using one or more TidyVerse packages, and any dataset from fivethirtyeight.com or Kaggle, create a programming sample “vignette” that demonstrates how to use one or more of the capabilities of the selected TidyVerse package with your selected dataset. (25 points) -> Magrittr package %>% 

```{r setup, include=FALSE}
library(tidyverse)
library(dplyr)
library(ggplot2)
library(magrittr)
```

Shark Attacks: The Risks of Coastal Water Activities
How to avoid shark attacks while swimming
dataset/ credit- https://www.sharkattackfile.net/incidentlog.htm

```{r} 
dfdata <- read.csv(file = 'https://raw.githubusercontent.com/marjete/607-APIs/main/GSAF5.xls.csv', header = TRUE)
```

#first 10 lines of code
```{r}
dfdata %>% head(n = 10)
```

##subset through selection in a column
```{r}
dfdata %>% subset(Type == "Provoked") %>% head
```

##arrange
```{r}
dfdata %>% arrange(Age)
```


##filter function below

```{r}
dfdata %>% filter(Injury == "FATAL") 
```


