---
title: "607 NYT API"
author: "Marjete Vucinaj"
date: "2022-10-30"
output:
  html_document: default
  pdf_document: default
---
Assignment – Web APIs
The New York Times web site provides a rich set of APIs, as described here: https://developer.nytimes.com/apis
You’ll need to start by signing up for an API key. Your task is to choose one of the New York Times APIs, construct an interface in R to read in the JSON data, and transform it into an R DataFrame.

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

```{r}
library(tidyverse)
library(dplyr)
library(ggplot2)
library(jsonlite)
library(stringr)
```


## API

```{r}
url <- "https://api.nytimes.com/svc/search/v2/articlesearch.json?q=election&api-key=yourkey"
api_key <- "N1sS2g6ji8HmCwjPfuGVz4QkHnUIj9oS" #personal API Key
api_path <- paste(url,api_key, sep = "")
```

I tried to read json data and insert it into R data frame- search.articles <- as.data.frame(fromJSON(api_path)) but #Error in open.connection(con, "rb") : HTTP error 401.


If there werent an error in the step above I would use summary, head/ colnames to review the data frame.


