---
title: "607 NYT API"
author: "Marjete Vucinaj"
date: "2022-10-30"
output:
  html_document: default
  pdf_document: default
---
# Assignment – Web APIs
The New York Times web site provides a rich set of APIs, as described here: https://developer.nytimes.com/apis
You’ll need to start by signing up for an API key. Your task is to choose one of the New York Times APIs, construct an interface in R to read in the JSON data, and transform it into an R DataFrame.

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
api_key <- "N1sS2g6ji8HmCwjPfuGVz4QkHnUIj9oS" #personal API Key
```

```{r}
library(tidyverse)
library(jsonlite)
library(httr)
```

# Get API 
```{r}
api_search <- "https://api.nytimes.com/svc/search/v2/articlesearch.json?q=election&api-key="
r <- GET(paste0(api_search, api_key))
status_code(r)

```
# Retrieve API 
```{r}
data <- content(r, as="text")
newdata <- fromJSON(data, flatten=TRUE) %>% data.frame()

colnames(newdata)

```
# Tidy Data
```{r}
df_news <- newdata %>%
select(response.docs.headline.main, response.meta.hits, response.docs.web_url,response.docs.pub_date)

```

```{r}
df_news %>%
rename("Headline" = 1, "Hits" = 2, "URL" = 3, "Date" = 4,)
```
### Odd observation that they all had the same number of hits

